### 2016-09-08 analysis-note-v2/analysis-2.tex
Clarification on calibration and clean up

~~~~In the previous chapter, the events were filtered to select the ones which have one and only one good electron, and other good particles in coincidence with the electron. This chapter explains the procedure we used to extract the beam-spin asymmetry observable following this order: clean the DVCS data sample by choosing good run list, ensure the exclusivity of the selected events by imposing the conservation laws, subtract the background by combining data with simulation, and binning the identified DVCS events. This chapter contains also an estimation of the systematic uncertainty contribution from each source on the measured beam-spin asymmetry.\\

@@

\section{Coherent channel}
\subsection{Good run list}
~~~~In principle, with constant beam luminosity, target density and pressure, the event rate has to be constant over the experimental time. Due to the changes in the experimental conditions, such as changing a trigger in a detector, a slight shift in the beam position or a system failure somewhere, this rate changes. We minimize the effects of these changes on the reconstructed events by selecting the good runs. To this aim, we monitor the ratio of the number of the good tracks reconstructed in the RTPC to number of the detected good electrons in CLAS (<tpc/e>) as a function of run number. Furthermore, we also look at this ratio in the six sectors of CLAS, as they are independent of each other and their performances might be different. \\

@@

~~~~Figure \ref{fig:tpc_over_e_Run_sec.png} shows the integrated and the 
sector-dependence of <tpc/e> for the individual runs. One notices a universal 
variation of this ratio over the three months of data taking. This can be 
attributed to changes in the RTPC. In particular, we had leaks in our gas 
system that appeared during the run. This probably caused gas contamination, 
changing the properties of the detector.

@@

\subsection{Coherent DVCS event selection}
~~~~Events with one and only one good electron, one and only one good RTPC 
track and at least one good photon are considered good coherent DVCS 
candidates. Even though the DVCS reaction has only one real photon in the final 
state, events with more than one good photon are not discarded at this stage.  
This is motivated by the fact that some photons correspond to random 
coincidences and discarding these events results in losing good events. Then, 
events with one or more $\pi^{0}$ are removed from the coherent DVCS sample.  
After that, the most energetic photon in each remaining event is chosen as the 
DVCS photon. Next, to consider an event as a clean $^{4}He$ DVCS, it has to 
pass respectively two sets of requirements: DVCS characteristic cuts and 
exclusivity cuts.

~\newpage
\paragraph{DVCS characteristics}
\begin{itemize}
 \item $Q^{2}$ > 1 GeV$^{2}$: to ensure that the interaction occurs at the 
    partonic level and the applicability of the factorization in the DVCS  
    handbag diagram.
\item $ -t > -t_{min}$: the transferred momentum squared to the recoil $^{4}He$ 
   has to be greater than a minimum value defined by the kinematics of the beam 
   and the scattered electron as:
\begin{equation}
   t_{min} = - Q^{2} \frac{2(1- x_{A})(1 - \sqrt{1 + \epsilon ^{2}}) + \epsilon 
   ^{2}}{4 x_{A}(1-x_{A})+ \epsilon ^{2}},\\
\end{equation}
where $\epsilon ^{2} = \frac{4M^{2}_{^4He}x^{2}_{A}}{Q^{2}}$, $x_{A} = 
\frac{M_{p}\cdot x_{B}}{M_{^4He}}$ and $M_{p}$ ($M_{^4He}$) is the proton 
($^{4}He$) mass.\\

@@

\newpage
\paragraph{Exclusivity cuts}

~\\
The coherent DVCS reaction is:
\begin{equation}
e(\mathbf{P}_{e}) + ~~^{4}He(\mathbf{P}_{^{4}He}) \rightarrow 
e'(\mathbf{P_{e'}}) +  ~~^{4}He'(\mathbf{P}_{^{4}He'}) + 
\gamma(\mathbf{P}_{\gamma})
\label{coh_dvcs_equ}
\end{equation}
where the symbols in the parentheses are the energy-momentum four-vectors. We define the additional four-vectors:
\begin{eqnarray}
\text{virtual photon vector } (\mathbf{P}_{\gamma^{*}}) &=&  \mathbf{P}_{e} -  \mathbf{P}_{e'} \\
\hspace{0.4in}  \mathbf{P}^{e^{4}He\gamma}_{X} &=& \mathbf{P}_{\gamma^{*}} + \mathbf{P}_{^{4}He} - (\mathbf{P}_{\gamma} + \mathbf{P}_{^{4}He'})\\
~~~~~~~~~~\mathbf{P}^{e^{4}He}_{X} &=& \mathbf{P}_{\gamma^{*}} + \mathbf{P}_{^{4}He} -  \mathbf{P}_{^{4}He'} \\
\hspace{0.2in} \mathbf{P}^{e\gamma}_{X} &=& \mathbf{P}_{\gamma^{*}} + \mathbf{P}_{^{4}He} - ~~\mathbf{P}_{\gamma}
\end{eqnarray}

~~~~The exclusivity of the coherent DVCS reaction is ensured by imposing the following conservation laws:
\begin{itemize}
\item The co-planarity cut ($\Delta \phi$). In principle, the virtual photon, the emitted real photon and the recoil helium lie in the same plane, which is called the hadronic plane. Thus the DVCS events must have $\Delta \phi$ values around zero. The hadronic plane can be defined in three ways:
\begin{eqnarray}
\overrightarrow{HP}_{1} &=& \overrightarrow{\mathbf{P}}_{^{4}He'} \times 
   \overrightarrow{\mathbf{P}}_{\gamma^{*}}\\
\overrightarrow{HP}_{2} &=& \overrightarrow{\mathbf{P}}_{^{4}He'}  \times 
   \overrightarrow{\mathbf{P}}_{\gamma}\\
\overrightarrow{HP}_{3} &=& \overrightarrow{\mathbf{P}}_{\gamma^{*}} \times 
   \overrightarrow{\mathbf{P}}_{\gamma}
\end{eqnarray}
$\Delta \phi$ is defined to be the $\phi$ difference between these planes and 
is calculable from three combinations: ($\overrightarrow{HP}_{1}$, 
$\overrightarrow{HP}_{2}$), ($\overrightarrow{HP}_{1}$, 
$\overrightarrow{HP}_{3}$) and ($\overrightarrow{HP}_{2}$, 
$\overrightarrow{HP}_{3}$). We investigated the three combinations and we 
decided to use the second one as it gives better resolution.

@@

\item Cone angle cut between the measured real photon and the missing particle 
   in the $e^{4}HeX$ configuration. It is defined as:
\begin{equation}
\theta(\gamma, e^{4}HeX) = cos^{-1} \left( 
\frac{\overrightarrow{\mathbf{P}}_{\gamma} \cdot 
\overrightarrow{\mathbf{P}}^{e^{4}He}_{X}}{|\overrightarrow{\mathbf{P}}_{\gamma^{}}| 
|\overrightarrow{\mathbf{P}}^{e^{4}He}_{X}|}   \right).
\end{equation}
\end{itemize}
~~~~~Figure \ref{fig:coh_exclusivty_cuts} summarizes all the exclusivity cuts.  
In these plots, the blue distributions represent the coherent events after the 
DVCS characteristic cuts and before all the exclusivity cuts. The shaded 
distributions stand for the events which passed all the exclusivity cuts except 
the one on the quantity plotted. We fitted each shaded distribution by a 
Gaussian and then we applied  3$\sigma$ cuts around the mean value of each 
distribution. The events which pass these cuts are assumed to be good $^{4}He$ 
DVCS events.  ~\\
~\\

@@

In this analysis We claim that kinematic exclusivity cuts are sufficient to
cleanly select coherent $^4$He DVCS events without the need for $\frac{dE}{dx}$
cuts. We performed few checks regarding applying a PID cut, where the full data
was analyzed in the following three sets:\\
\begin{itemize}
\item Processing all the reconstructed tracks in each event with the exclusivity
cuts.\\
\item Processing events with only one good track in the RTPC being
reconstructed.\\
\item Processing events with only one track that passes a dedx cut.\\
\end{itemize}

@@

\subsection{Comparison with simulation}
~~~~Coherent DVCS events were simulated according to the procedures described 
in section \ref{Event_generator}. Then, events are selected following the same 
identification criteria as for the experimental data. Finally, We apply similar 
exclusivity cuts as presented for the experimental coherent DVCS events. That 
is each exclusive distribution is fitted by a Gaussian and a 3$\sigma$ cut is 
applied. So the cut are not identical, but obtained with the same method. This 
is done to avoid issues on variables where the peak is not in the exact same 
place in simulation and in data.\\

@@

\section{Incoherent channel}
~~~~In this channel, the DVCS process happens on a bound proton. Thus, the 
final state has a recoil proton instead of the helium nucleus. Therefore, 
events with one good electron, one recoil proton, and at least one real photon 
are the good candidates here. For the rest, we follow the same steps that were 
introduced for the coherent DVCS selection.

\subsection{Good run list}
~~~~The events rate stability is verified by looking at the rate of the 
detected number of protons to the detected electrons (<p/e>). Like for the 
coherent channel, the same technique for the determination of the good run list 
is followed herein. The results are presented in figure 
\ref{fig:prot_over_e_Run_sec.png}.  \begin{figure}[h!]
\includegraphics[scale=0.4]{fig_dvcs/prot_over_e_Run.png}
\includegraphics[scale=0.4]{fig_dvcs/prot_over_e_Run_sec.png}
\caption{On the top: the integrated <$p/e$> ratio as a function of run number.  
   The blue points refer to the good runs, while the black points are the 
rejected ones. On the bottom: the same ratio for each run, is shown for each 
sector of CLAS. The colored points indicate the six sectors, while the black 
points are the sectors of the rejected runs. } 
\label{fig:prot_over_e_Run_sec.png}
\end{figure}

\subsection{Proton DVCS event selection}
~~~~To certify that an event is a proton DVCS one, we require the same DVCS 
kinematic cuts as those presented for the coherent DVCS selection. Then, the 
exclusivity of the DVCS reaction is ensured by applying an equivalent set of 
exclusivity with taking a proton at rest as the target, instead of $^4He$.  
Figure \ref{fig:incoh_exclusivty_cuts} summarizes these exclusivity cuts.\\

@@

\subsection{Comparison with simulation}
~~~~The three particles of the simulated $ep\gamma$ DVCS events are selected 
applying the previously described identification requirements. The events with 
three identified particles (e, p, $\gamma$) are required to pass a set of 
exclusivity cuts such as the ones of the experimental incoherent DVCS events.  
In this section, a comparison between the experimental and the simulated data 
is carried out.\\

@@

~\newpage
~\newpage
\section{Kinematic coverages}
~~~~The one-dimensional distributions of explored kinematical regions can be 
seen in figure \ref{fig:coh_comparison_with_simulation_1} for the coherent, and 
in figure \ref{fig:incoh_coparison_with_simulation_1} for the incoherent DVCS 
channels. In figure \ref{fig:kinematic_coverage}, we show two-dimensional 
distributions of these variables to display the correlations between them. 
%\begin {table}[!h]
%\begin{center}
%\begin{tabular}{|l|l|l|l|}
%\hline
%DVCS channel &  $Q^{2}$~$[GeV^{2}/c^{2}]$  & $~~~~~~x_{B}$  & -t ~$[GeV^{2}/c^{2}]$\\
%\hline
%Helium-4 & [1.0, 3.0] & [0.1, 0.3] & [0.06, 0.2] \\
%\hline
%proton & [1.0, 4.5] & [0.1, 0.55] & [0.03, 2.5] \\
%\hline
%\end{tabular}
%\caption{ The coherent and the incoherent explored kinematic regions.}
%\label{Table:kinematic_ranges}
%\end{center}
%\end{table}

@@

\section{Data binning}
~~~~~The DVCS cross section and $A_{LU}$, equations \ref{BSA_equation} to 
\ref{eq:A_LU-coh}, depend on the four kinematic variables: $Q^{2}$, $x_{B}$, 
$t$, and $\phi$. The number of identified coherent (incoherent) DVCS events is 
about 5000 (30k). Due to our limited statistics only, a two-dimensional binning 
is carried out in this analysis.  The strongest dependence of $A_{LU}$ is on 
the azimuthal angle between the leptonic and the hadronic planes ($\phi$).  
Thus, we construct the two-dimensional bins as follows: the coherent 
(incoherent) measured ranges of $Q^{2}$, $x_{B}$ and $-t$ are binned 
statistically into three (four) bins.  Then, the identified DVCS events in each 
$Q^{2}$, $x_{B}$ and $-t$ bin, are binned into nine bins in $\phi$.  Therefore, 
we are left with $Q^2$-$\phi$ bins integrated over the full ranges of $x_{B}$ 
and $-t$, $x_{B}$-$\phi$ bins integrated over $Q^2$ and $-t$, and $-t$-$\phi$ 
bins integrated over $Q^2$ and $x_{B}$. For instance, figure 
\ref{fig:coh_Q2_bins} shows the one-dimensional bins in $Q^2$ and the 
associated bins in $\phi$.

@@

\subsection{$\pi^0$ contaminations}
~~~~Even with all cuts applied to select the selected DVCS events, the events 
are not all DVCS events. In our kinematic region, the main contamination comes 
from the exclusive electroproduction of $\pi^{0}$ ($e ^{4}He \rightarrow e 
^{4}He \pi^{0} \rightarrow e ^{4}He \gamma \gamma $, $e p \rightarrow e p 
\pi^{0} \rightarrow e p \gamma \gamma $), in which one of the two photons of 
the $\pi^{0}$ decay passes the requirements of the DVCS. Thus, the event is 
counted as a DVCS event. These events contaminate the DVCS sample and have to 
be subtracted to obtain the true number of DVCS events. In the case of the 
coherent channel, this can be formulated as:
\begin{equation}
N^{True}_{e^{4}He\gamma} = N^{Exp.}_{e^{4}He\gamma} -  N^{Exp.}_{e^{4}He\pi^{0}(\gamma)},
\label{equ_back_1}
\end{equation}
where $N^{True}_{e^{4}He\gamma}$, $N^{Exp.}_{e^{4}He\gamma}$ and $ 
N^{Exp.}_{e^{4}He\pi^{0}(\gamma)}$ are the true number of coherent DVCS events, 
the experimentally measured number of $e^{4}He\gamma$ events and the 
contamination number, respectively. The contamination can be calculated by 
using real data and simulation. We define, for each kinematic bin and for each 
beam helicity state
\begin{equation}
N^{Exp.}_{e^{4}He\pi^{0}(\gamma)} = 
\frac{N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}}{N^{Sim.}_{e^{4}He\pi^{0}(\gamma 
\gamma)}} * N^{Exp.}_{e^{4}He\pi^{0}(\gamma \gamma)},
\label{equation: background_equ}
\end{equation}
where $N^{Exp.}_{e^{4}He\pi^{0}(\gamma \gamma)}$ is the number of measured 
$e^{4}He\pi^{0}$ events, for which both photons of the $\pi^{0}$ have been 
detected. The quantity 
$\frac{N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}}{N^{Sim.}_{e^{4}He\pi^{0}(\gamma 
\gamma)}} $ is the acceptance ratio for detecting a $e^{4}He\gamma$ event that 
originates from an $e^{4}He\pi^{0}$ event. It can be derived from Monte-Carlo 
simulations by generating and simulating $e^{4}He\pi^{0}$.  
$N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}$ is the number of such events passing the 
DVCS requirements, while $N^{Sim.}_{e^{4}He\pi^{0}(\gamma \gamma)}$ is the 
number of simulated $e^{4}He\pi^{0}$ events passing the exclusivity cuts for 
$e^{4}He\pi^{0}$ events.\\

The previous formulas apply to the case of the coherent DVCS. The same 
procedures hold for the incoherent case by replacing the $^{4}He$ with the 
proton.\\

The selection of the exclusive $e^{4}He\pi^{0}$ and $ep\pi^{0}$ events requires 
the detection of one good electron, one good $\pi^{0}$ in the topology ICIC or 
ICEC, and one good $^{4}He$ track in the coherent case, or one good proton in 
the incoherent case. In order to ensure that this is a deep process, we apply 
the same kinematic cuts as DVCS. These cuts and the comparisons with simulation 
can be found in Appendix \ref{app:Exclusive_pi0_selection}.\\

Figure \ref{fig:coh_acceptance _ratios} shows the coherent acceptance ratio as 
a function of each of the four kinematic variables ($Q^{2}$, $x_{B}$, $-t$, 
$\phi_{h}$). These distributions are one-dimensional, i.e. the data are 
integrated over all kinematical ranges except for the quantity which is binned 
(along the x-axis). The results for the incoherent channel can be found in 
figure \ref{fig:incoh_acceptance _ratios}. The mean value of the acceptance 
ratio for the coherent channel is around 25$\%$, with some dependence on 
$x_{B}$ and $\phi$, and almost no dependence on $Q^{2}$ and $-t$. For the 
incoherent channel, the mean acceptance ratio is around 20$\%$ with some 
dependence on the four kinematic variables.\\

Figure \ref{fig:cont_yield} presents the measured coherent and incoherent 
$\pi^{0}$ contmaination with respect to the measured DVCS events. On both 
channels, the contamination increases strongly with -$t$, with a mean of 2$\%$ 
(6$\%$) for the coherent (incoherent) channel. \\

@@

\subsection{Accidental contaminations}
~\\

The $\Delta z$ distributions between the recoil hadrons and the scattered 
electrons, see figures \ref{fig:rtpc_delta_z} and 
\ref{fig:proton_delta_z_e_prot}, indicate that accidental background events are 
contributing inside the exclusive DVCS. In order to estimate and correct 
this background contribution, we processed our dataset with the previously 
presented exclusive requirements without any constraints on the z-vertex of the 
final state particle nor on the correspondence between them, $\Delta z$. The 
results for the identified coherent DVCS events are presented in figure 
\ref{fig:delta_z_after_ex}. This guides us to correct for these accidentals in 
our asymmetries in the form: $ A_{LU~~corr.} = \frac{1}{1 - contamination} 
A_{LU}$, with a 4.1$\%$ global accidental contamination for the coherent DVCS 
channel (see numbers in table~\ref{table:Events_numbers}). The same procedures 
were performed on the incoherent channel, and a 
global contamination of 6.5$\%$ has been observed.\\

@@

\paragraph{Acceptance ratio}
~\\

>>>>

In the previous chapter, the events were filtered to select the ones which have one and only one good electron, and other good particles in coincidence with the electron. This chapter explains the procedure we used to extract the beam-spin asymmetry observable following this order: clean the DVCS data sample by choosing good run list, ensure the exclusivity of the selected events by imposing the conservation laws, subtract the background by combining data with simulation, and binning the identified DVCS events. This chapter contains also an estimation of the systematic uncertainty contribution from each source on the measured beam-spin asymmetry.

@@

\section{Coherent channel}
\subsection{Good run list}
In principle, with constant beam luminosity, target density and pressure, the event rate has to be constant over the experimental time. Due to the changes in the experimental conditions, such as changing a trigger in a detector, a slight shift in the beam position or a system failure somewhere, this rate changes. We minimize the effects of these changes on the reconstructed events by selecting the good runs. To this aim, we monitor the ratio of the number of the good tracks reconstructed in the RTPC to number of the detected good electrons in CLAS (<tpc/e>) as a function of run number. Furthermore, we also look at this ratio in the six sectors of CLAS, as they are independent of each other and their performances might be different.

@@

Figure \ref{fig:tpc_over_e_Run_sec.png} shows the integrated and the 
sector-dependence of <tpc/e> for the individual runs. One notices a universal 
variation of this ratio over the three months of data taking. This can be 
attributed to changes in the RTPC. In particular, we had leaks in our gas 
system that appeared during the run. This probably caused gas contamination, 
changing the properties of the detector.

@@

\subsection{Coherent DVCS event selection}
Events with one and only one good electron, one and only one good RTPC 
track and at least one good photon are considered good coherent DVCS 
candidates. Even though the DVCS reaction has only one real photon in the final 
state, events with more than one good photon are not discarded at this stage.  
This is motivated by the fact that some photons correspond to random 
coincidences and discarding these events results in losing good events. Then, 
events with one or more $\pi^{0}$ are removed from the coherent DVCS sample.  
After that, the most energetic photon in each remaining event is chosen as the 
DVCS photon. Next, to consider an event as a clean $^{4}He$ DVCS, it has to 
pass respectively two sets of requirements: DVCS characteristic cuts and 
exclusivity cuts.

~\newpage
\paragraph{DVCS characteristics}
\begin{itemize}
 \item $Q^{2}$ > 1 GeV$^{2}$: to ensure that the interaction occurs at the 
    partonic level and the applicability of the factorization in the DVCS  
    handbag diagram.
\item $ -t > -t_{min}$: the transferred momentum squared to the recoil $^{4}He$ 
   has to be greater than a minimum value defined by the kinematics of the beam 
   and the scattered electron as:
\begin{equation}
   t_{min} = - Q^{2} \frac{2(1- x_{A})(1 - \sqrt{1 + \epsilon ^{2}}) + \epsilon 
   ^{2}}{4 x_{A}(1-x_{A})+ \epsilon ^{2}},\\
\end{equation}
where $\epsilon ^{2} = \frac{4M^{2}_{^4He}x^{2}_{A}}{Q^{2}}$, $x_{A} = 
\frac{M_{p}\cdot x_{B}}{M_{^4He}}$ and $M_{p}$ ($M_{^4He}$) is the proton 
($^{4}He$) mass.

@@

\newpage
\paragraph{Exclusivity cuts} ~\\
The coherent DVCS reaction is:
\begin{equation}
e(\mathbf{P}_{e}) + ~~^{4}He(\mathbf{P}_{^{4}He}) \rightarrow 
e'(\mathbf{P_{e'}}) +  ~~^{4}He'(\mathbf{P}_{^{4}He'}) + 
\gamma(\mathbf{P}_{\gamma})
\label{coh_dvcs_equ}
\end{equation}
where the symbols in the parentheses are the energy-momentum four-vectors. We define the additional four-vectors:
\begin{eqnarray}
\text{virtual photon vector } (\mathbf{P}_{\gamma^{*}}) &=&  \mathbf{P}_{e} -  \mathbf{P}_{e'} \\
\hspace{0.4in}  \mathbf{P}^{e^{4}He\gamma}_{X} &=& \mathbf{P}_{\gamma^{*}} + \mathbf{P}_{^{4}He} - (\mathbf{P}_{\gamma} + \mathbf{P}_{^{4}He'})\\
~~~~~~~~~~\mathbf{P}^{e^{4}He}_{X} &=& \mathbf{P}_{\gamma^{*}} + \mathbf{P}_{^{4}He} -  \mathbf{P}_{^{4}He'} \\
\hspace{0.2in} \mathbf{P}^{e\gamma}_{X} &=& \mathbf{P}_{\gamma^{*}} + \mathbf{P}_{^{4}He} - ~~\mathbf{P}_{\gamma}
\end{eqnarray}

The exclusivity of the coherent DVCS reaction is ensured by imposing the following conservation laws:
\begin{itemize}
\item The co-planarity cut ($\Delta \phi$). In principle, the virtual photon, the emitted real photon and the recoil helium lie in the same plane, which is called the hadronic plane. Thus the DVCS events must have $\Delta \phi$ values around zero. The hadronic plane can be defined in three ways:
\begin{eqnarray}
\overrightarrow{HP}_{1} &=& \overrightarrow{\mathbf{P}}_{^{4}He'} \times 
   \overrightarrow{\mathbf{P}}_{\gamma^{*}}\\
\overrightarrow{HP}_{2} &=& \overrightarrow{\mathbf{P}}_{^{4}He'}  \times 
   \overrightarrow{\mathbf{P}}_{\gamma}\\
\overrightarrow{HP}_{3} &=& \overrightarrow{\mathbf{P}}_{\gamma^{*}} \times 
   \overrightarrow{\mathbf{P}}_{\gamma}
\end{eqnarray}
$\Delta \phi$ is defined to be the $\phi$ difference between these planes and 
is calculable from three combinations: ($\overrightarrow{HP}_{1}$, 
$\overrightarrow{HP}_{2}$), ($\overrightarrow{HP}_{1}$, 
$\overrightarrow{HP}_{3}$) and ($\overrightarrow{HP}_{2}$, 
$\overrightarrow{HP}_{3}$). We investigated the three combinations and we 
decided to use the second one as it gives better resolution.

@@

\item Cone angle cut between the measured real photon and the missing particle 
   in the $e^{4}HeX$ configuration. It is defined as:
\begin{equation}
\theta(\gamma, e^{4}HeX) = cos^{-1} \left( 
\frac{\overrightarrow{\mathbf{P}}_{\gamma} \cdot 
\overrightarrow{\mathbf{P}}^{e^{4}He}_{X}}{|\overrightarrow{\mathbf{P}}_{\gamma^{}}| 
|\overrightarrow{\mathbf{P}}^{e^{4}He}_{X}|}   \right).
\end{equation}
\end{itemize}
Figure \ref{fig:coh_exclusivty_cuts} summarizes all the exclusivity cuts.  
In these plots, the blue distributions represent the coherent events after the 
DVCS characteristic cuts and before all the exclusivity cuts. The shaded 
distributions stand for the events which passed all the exclusivity cuts except 
the one on the quantity plotted. We fitted each shaded distribution by a 
Gaussian and then we applied  3$\sigma$ cuts around the mean value of each 
distribution. The events which pass these cuts are assumed to be good $^{4}He$ 
DVCS events.

@@

In this analysis We claim that kinematic exclusivity cuts are sufficient to
cleanly select coherent $^4$He DVCS events without the need for $\frac{dE}{dx}$
cuts. We performed few checks regarding applying a PID cut, where the full data
was analyzed in the following three sets:
\begin{itemize}
\item Processing all the reconstructed tracks in each event with the exclusivity
cuts.
\item Processing events with only one good track in the RTPC being
reconstructed.
\item Processing events with only one track that passes a dedx cut.
\end{itemize}

@@

\subsection{Comparison with simulation}
Coherent DVCS events were simulated according to the procedures described 
in section \ref{Event_generator}. Then, events are selected following the same 
identification criteria as for the experimental data. Finally, We apply similar 
exclusivity cuts as presented for the experimental coherent DVCS events. That 
is each exclusive distribution is fitted by a Gaussian and a 3$\sigma$ cut is 
applied. So the cut are not identical, but obtained with the same method. This 
is done to avoid issues on variables where the peak is not in the exact same 
place in simulation and in data.

@@

\section{Incoherent channel}
In this channel, the DVCS process happens on a bound proton. Thus, the 
final state has a recoil proton instead of the helium nucleus. Therefore, 
events with one good electron, one recoil proton, and at least one real photon 
are the good candidates here. For the rest, we follow the same steps that were 
introduced for the coherent DVCS selection.

\subsection{Good run list}
The events rate stability is verified by looking at the rate of the 
detected number of protons to the detected electrons (<p/e>). Like for the 
coherent channel, the same technique for the determination of the good run list 
is followed herein. The results are presented in figure 
\ref{fig:prot_over_e_Run_sec.png}.  \begin{figure}[h!]
\includegraphics[scale=0.4]{fig_dvcs/prot_over_e_Run.png}
\includegraphics[scale=0.4]{fig_dvcs/prot_over_e_Run_sec.png}
\caption{On the top: the integrated <$p/e$> ratio as a function of run number.  
   The blue points refer to the good runs, while the black points are the 
rejected ones. On the bottom: the same ratio for each run, is shown for each 
sector of CLAS. The colored points indicate the six sectors, while the black 
points are the sectors of the rejected runs. } 
\label{fig:prot_over_e_Run_sec.png}
\end{figure}

\subsection{Proton DVCS event selection}
To certify that an event is a proton DVCS one, we require the same DVCS 
kinematic cuts as those presented for the coherent DVCS selection. Then, the 
exclusivity of the DVCS reaction is ensured by applying an equivalent set of 
exclusivity with taking a proton at rest as the target, instead of $^4He$.  
Figure \ref{fig:incoh_exclusivty_cuts} summarizes these exclusivity cuts.

@@

\subsection{Comparison with simulation}
The three particles of the simulated $ep\gamma$ DVCS events are selected 
applying the previously described identification requirements. The events with 
three identified particles (e, p, $\gamma$) are required to pass a set of 
exclusivity cuts such as the ones of the experimental incoherent DVCS events.  
In this section, a comparison between the experimental and the simulated data 
is carried out.

@@

~\newpage
~\newpage
\section{Kinematic coverages}
The one-dimensional distributions of explored kinematical regions can be 
seen in figure \ref{fig:coh_comparison_with_simulation_1} for the coherent, and 
in figure \ref{fig:incoh_coparison_with_simulation_1} for the incoherent DVCS 
channels. In figure \ref{fig:kinematic_coverage}, we show two-dimensional 
distributions of these variables to display the correlations between them. 
%\begin {table}[!h]
%\begin{center}
%\begin{tabular}{|l|l|l|l|}
%\hline
%DVCS channel &  $Q^{2}$~$[GeV^{2}/c^{2}]$  & $~~~~~~x_{B}$  & -t ~$[GeV^{2}/c^{2}]$\\
%\hline
%Helium-4 & [1.0, 3.0] & [0.1, 0.3] & [0.06, 0.2] \\
%\hline
%proton & [1.0, 4.5] & [0.1, 0.55] & [0.03, 2.5] \\
%\hline
%\end{tabular}
%\caption{ The coherent and the incoherent explored kinematic regions.}
%\label{Table:kinematic_ranges}
%\end{center}
%\end{table}

@@

\section{Data binning}
The DVCS cross section and $A_{LU}$, equations \ref{BSA_equation} to 
\ref{eq:A_LU-coh}, depend on the four kinematic variables: $Q^{2}$, $x_{B}$, 
$t$, and $\phi$. The number of identified coherent (incoherent) DVCS events is 
about 5000 (30k). Due to our limited statistics only, a two-dimensional binning 
is carried out in this analysis.  The strongest dependence of $A_{LU}$ is on 
the azimuthal angle between the leptonic and the hadronic planes ($\phi$).  
Thus, we construct the two-dimensional bins as follows: the coherent 
(incoherent) measured ranges of $Q^{2}$, $x_{B}$ and $-t$ are binned 
statistically into three (four) bins.  Then, the identified DVCS events in each 
$Q^{2}$, $x_{B}$ and $-t$ bin, are binned into nine bins in $\phi$.  Therefore, 
we are left with $Q^2$-$\phi$ bins integrated over the full ranges of $x_{B}$ 
and $-t$, $x_{B}$-$\phi$ bins integrated over $Q^2$ and $-t$, and $-t$-$\phi$ 
bins integrated over $Q^2$ and $x_{B}$. For instance, figure 
\ref{fig:coh_Q2_bins} shows the one-dimensional bins in $Q^2$ and the 
associated bins in $\phi$.

@@

\subsection{$\pi^0$ contaminations}
Even with all cuts applied to select the selected DVCS events, the events 
are not all DVCS events. In our kinematic region, the main contamination comes 
from the exclusive electroproduction of $\pi^{0}$ ($e ^{4}He \rightarrow e 
^{4}He \pi^{0} \rightarrow e ^{4}He \gamma \gamma $, $e p \rightarrow e p 
\pi^{0} \rightarrow e p \gamma \gamma $), in which one of the two photons of 
the $\pi^{0}$ decay passes the requirements of the DVCS. Thus, the event is 
counted as a DVCS event. These events contaminate the DVCS sample and have to 
be subtracted to obtain the true number of DVCS events. In the case of the 
coherent channel, this can be formulated as:
\begin{equation}
N^{True}_{e^{4}He\gamma} = N^{Exp.}_{e^{4}He\gamma} -  N^{Exp.}_{e^{4}He\pi^{0}(\gamma)},
\label{equ_back_1}
\end{equation}
where $N^{True}_{e^{4}He\gamma}$, $N^{Exp.}_{e^{4}He\gamma}$ and $ 
N^{Exp.}_{e^{4}He\pi^{0}(\gamma)}$ are the true number of coherent DVCS events, 
the experimentally measured number of $e^{4}He\gamma$ events and the 
contamination number, respectively. The contamination can be calculated by 
using real data and simulation. We define, for each kinematic bin and for each 
beam helicity state
\begin{equation}
N^{Exp.}_{e^{4}He\pi^{0}(\gamma)} = 
\frac{N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}}{N^{Sim.}_{e^{4}He\pi^{0}(\gamma 
\gamma)}} * N^{Exp.}_{e^{4}He\pi^{0}(\gamma \gamma)},
\label{equation: background_equ}
\end{equation}
where $N^{Exp.}_{e^{4}He\pi^{0}(\gamma \gamma)}$ is the number of measured 
$e^{4}He\pi^{0}$ events, for which both photons of the $\pi^{0}$ have been 
detected. The quantity 
$\frac{N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}}{N^{Sim.}_{e^{4}He\pi^{0}(\gamma 
\gamma)}} $ is the acceptance ratio for detecting a $e^{4}He\gamma$ event that 
originates from an $e^{4}He\pi^{0}$ event. It can be derived from Monte-Carlo 
simulations by generating and simulating $e^{4}He\pi^{0}$.  
$N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}$ is the number of such events passing the 
DVCS requirements, while $N^{Sim.}_{e^{4}He\pi^{0}(\gamma \gamma)}$ is the 
number of simulated $e^{4}He\pi^{0}$ events passing the exclusivity cuts for 
$e^{4}He\pi^{0}$ events.

The previous formulas apply to the case of the coherent DVCS. The same 
procedures hold for the incoherent case by replacing the $^{4}He$ with the 
proton.

The selection of the exclusive $e^{4}He\pi^{0}$ and $ep\pi^{0}$ events requires 
the detection of one good electron, one good $\pi^{0}$ in the topology ICIC or 
ICEC, and one good $^{4}He$ track in the coherent case, or one good proton in 
the incoherent case. In order to ensure that this is a deep process, we apply 
the same kinematic cuts as DVCS. These cuts and the comparisons with simulation 
can be found in Appendix \ref{app:Exclusive_pi0_selection}.

Figure \ref{fig:coh_acceptance _ratios} shows the coherent acceptance ratio as 
a function of each of the four kinematic variables ($Q^{2}$, $x_{B}$, $-t$, 
$\phi_{h}$). These distributions are one-dimensional, i.e. the data are 
integrated over all kinematical ranges except for the quantity which is binned 
(along the x-axis). The results for the incoherent channel can be found in 
figure \ref{fig:incoh_acceptance _ratios}. The mean value of the acceptance 
ratio for the coherent channel is around 25$\%$, with some dependence on 
$x_{B}$ and $\phi$, and almost no dependence on $Q^{2}$ and $-t$. For the 
incoherent channel, the mean acceptance ratio is around 20$\%$ with some 
dependence on the four kinematic variables.

Figure \ref{fig:cont_yield} presents the measured coherent and incoherent 
$\pi^{0}$ contmaination with respect to the measured DVCS events. On both 
channels, the contamination increases strongly with -$t$, with a mean of 2$\%$ 
(6$\%$) for the coherent (incoherent) channel.

@@

\subsection{Accidental contaminations}

The $\Delta z$ distributions between the recoil hadrons and the scattered 
electrons, see figures \ref{fig:rtpc_delta_z} and 
\ref{fig:proton_delta_z_e_prot}, indicate that accidental background events are 
contributing inside the exclusive DVCS. In order to estimate and correct 
this background contribution, we processed our dataset with the previously 
presented exclusive requirements without any constraints on the z-vertex of the 
final state particle nor on the correspondence between them, $\Delta z$. The 
results for the identified coherent DVCS events are presented in figure 
\ref{fig:delta_z_after_ex}. This guides us to correct for these accidentals in 
our asymmetries in the form: $ A_{LU~~corr.} = \frac{1}{1 - contamination} 
A_{LU}$, with a 4.1$\%$ global accidental contamination for the coherent DVCS 
channel (see numbers in table~\ref{table:Events_numbers}). The same procedures 
were performed on the incoherent channel, and a 
global contamination of 6.5$\%$ has been observed.

@@

\paragraph{Acceptance ratio} ~\\
Predominantly, two techniques are used to estimate the systematic uncertainty 
associated with the calculated acceptance ratio (R). The first is via repeating 
the analysis by implementing R differently, while the second technique is by 
using two generating models to calculate R.
